Party tricks for PostgreSQL \\ perf, ftrace and bpftrace

### 2022-10-26 pgconfeu2022/presentation.tex
Modifiers
kfuncs + flamegraphs

@@

>>>>

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        Dynamic tracing: k[ret]probe vs k[ret]func
    \end{center}
\end{frame}
\note{
    maxactive patch, shadow stack improvements
}

@@

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \begin{minted}[fontsize=\large]{shell-session}
$ perf record -e event:[u:k:pp:b]
        \end{minted}
    \end{center}
\end{frame}
\note{Duplicated functions?}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \begin{minted}[fontsize=\large]{shell-session}
$ perf record -F max | -c 1000
$ perf script
$ stackcollapse-perf.pl
$ flamegraph.pl --hash
        \end{minted}
    \end{center}
\end{frame}
\note{
    Frequency vs event sample period, inconsistency with flamegraph
}
